%-----------------------------------------------------------------------------%
\pagebreak
\section*{Project Schedule}

Legend:
\begin{itemize}
    \item (\checkmark)  Complete
    \item (\checkmark-)  Underway but incomplete
    \item ($\cdot$)  Not started
\end{itemize}


\begin{enumerate}
\item \textbf{(\checkmark-) Literature review.}
\item \textbf{(\checkmark) Develop CFD-CRUD tools for training data generation and extraction.}
          Platform used to generate datasets that are
          required to inform a scale-bridging model.
    \begin{enumerate}
        \item (\checkmark) Create CFD data extraction and post processing utilities.
        \item (\checkmark) Develop STAR-CCM+ plugin to extract cladding surface and volumetric TH quantities from a CFD computation.
        \item (\checkmark) Compute the required volume and surface integrals to
              distill finely resolved CFD datasets into subchannel-like results.
    \end{enumerate}
\item \textbf{(\checkmark-) Demonstrate differences between CFD and Subchannel predictions.}
    \begin{enumerate}
        \item (\checkmark-) Compute differences between volume/surface averaged CFD quantities and subchannel predictions.
        \item ($\cdot$) Identify deficiencies in subchannel predictions wrt. CRUD growth and CILC.
    \end{enumerate}
\item \textbf{(\checkmark-) Investigate CRUD model sensitives.}
    \begin{enumerate}
        \item (\checkmark) Identify CRUD (MAMBA) sensitivities to TH boundary conditions
        \item (\checkmark) Produce correlation coefficients and scatter plot depictions of the relationship(s) between input
              and output of the CRUD model.
          \item (\checkmark-) Identify TH conditions under which CFD scale CRUD predictions diverge from subchannel-CRUD results.
    \end{enumerate}
\item \textbf{(\checkmark-) Preliminary methods implementation and demonstration}
    \begin{enumerate}
        \item (\checkmark-) De-trend pointwise CFD datasets \& compute residual distributions.
        \begin{enumerate}
            \item (\checkmark) Moving averaged approach (assumes CTF and CFD will agree on the mean)
            \item (\checkmark-) CTF mean approach (requires CTF runs at identical CFD sample points)
        \end{enumerate}
        %
        \item (\checkmark) Create a tool to generate synthetic CFD-like training data sets to facilitate
            testing of the regression tools.
        %
        \item (\checkmark) Construct model of the spatially dependent co-variance between
              (residual) wall temperatures, surface shear stress, and
              boundary heat flux downstream of a grid span.
        \begin{enumerate}
            \item (\checkmark) Develop flexible dependence modeling package capable of capturing skewed covariance behavior (Copula).
            \item ($\cdot$) Develop Kriging model to capture spatial auto-correlation (may not be necessary?).
        \end{enumerate}
        %
        \item (\checkmark) Construct a regression model $G(\cdot)$ (Gradient boosted tree model [GBM]).
        \begin{enumerate}
            \item (\checkmark) Regress copula model parameters, $\bm{\hat\theta}$, on local-average CTF provided inputs.
            \item (\checkmark) Evaluate regression to recover joint TH distributions on any CDF patch:
                $G(CTF\ Patch\ Data) \rightarrow {P(T>t,TKE>tke,...|\bm{\hat\theta})}$
        \end{enumerate}
        %
        \item ($\cdot$) Uncertainty Propagation
        \begin{enumerate}
        	\item ($\cdot$) How many quantiles are required for temperature and TKE margin reconstruction 
        		- do we have the data required to drive down uncertainty in CRUD predictions to an acceptible level?
            \item ($\cdot$) Estimate uncertainty introduced by the GBRT/Copula model
            \item ($\cdot$) Propogate uncertainty to ensemble CRUD calculations
        \end{enumerate}
        %----------------- POST PROPOSAL ------------------%
        \item (\checkmark-) (\checkmark-) Multi-state point execution
        \begin{enumerate}
            \item (\checkmark-) Implement time stepping scheme
            \item ($\cdot$) Propagate uncertainty through time steps
        \end{enumerate}
        % -------------------------------------------------%
        \item ($\cdot$) Compute areas of the prediction surface with highest
            sensitivity to changes in input parameters \& develop capability to super sample these regions.
        %
        \item ($\cdot$) Demonstrate ability to perform dimensionality reduction of the input space via PCA.
        \item (\checkmark-) Perform CFD informed subchannel based CRUD prediction for a \emph{single pin}.
    \end{enumerate}
\item \textbf{(\checkmark-) Write proposal document}
\item \textbf{($\cdot$) Methods analysis and improvement}
    \begin{enumerate}
        \item ($\cdot$) Perform Large scale CFD runs to inform finalized scale-bridging model
        \item ($\cdot$) Tune regression algorithm's (GBM) hyperparameters
        \item ($\cdot$) Validate CFD informed subchannel CRUD results against plant data (IF AVAILABLE).
    \end{enumerate}
\item \textbf{($\cdot$) Final model construction and demonstration}
    \begin{enumerate}
        \item ($\cdot$) Demonstrate CFD informed subchannel model on a full-height, single assembly problem.
        \item ($\cdot$) Assess CILC/CIPS prediction improvements vs. base model (no CFD informed TH).
    \end{enumerate}
\item \textbf{($\cdot$) Write Dissertation}
\end{enumerate}

\begin{sidewaysfigure}
%---------------------------     YEAR ONE        ------------------------------%
\begin{ganttchart}[
        inline,
        x unit=1.5cm,
        y unit title =0.8cm,
        y unit chart=0.8cm,
        hgrid,
        vgrid,
        time slot format=isodate,
        compress calendar
    ]{2016-06-01}{2017-07-30}
    \gantttitlecalendar*[compress calendar, time slot format=isodate]{2016-06-01}{2017-07-30}{year, month=shortname} \\
    \gantttitlelist{1,...,14}{1} \\
%%%%%%% Phase 1
\ganttgroup{Proposal Era}{2016-06-01}{2017-06-30} \\  %elem0
\ganttbar{Lit. Review}{2016-06-01}{2016-11-01} \\  %elem1
\ganttbar{CFD Post Proc. Dev.}{2016-06-01}{2016-08-20} \\  %elem2
\ganttlinkedbar{CTF vs CFD}{2016-08-20}{2016-10-30} \ganttnewline  %elem3
\ganttbar{MAMBA Sensitivity}{2016-08-01}{2016-09-30} \ganttnewline  %elem4
\ganttbar{Copula Model Dev.}{2016-10-01}{2017-01-10}  \\  %elem5
\ganttbar{Synthetic Data Gen}{2016-12-01}{2017-01-30} \\  %elem6
\ganttlinkedbar{GBRT Model Dev.}{2016-12-01}{2017-03-30}  \\  %elem7
\ganttlinkedbar{Link Models w/ CRUD Sim.}{2017-03-01}{2017-06-30}  \\  %elem8
\ganttbar{Write Proposal}{2017-04-01}{2017-06-30}  %elem9
\ganttmilestone{Proposal}{2017-06-30} \ganttnewline  %elem10
%%%%%%%% Extra Task Linkages
\ganttlink[link mid=0.2]{elem2}{elem4}
\end{ganttchart}
%-----------------------------------------------------------------------------%
\end{sidewaysfigure}

\begin{sidewaysfigure}
%---------------------------     YEAR TWO       ------------------------------%
\begin{ganttchart}[
        inline,
        x unit=2.5cm,
        y unit title =0.8cm,
        y unit chart=0.8cm,
        hgrid,
        vgrid,
        time slot format=isodate,
        compress calendar
    ]{2017-06-01}{2018-01-30}
    \gantttitlecalendar*[compress calendar, time slot format=isodate]{2017-06-01}{2018-01-30}{year, month=shortname} \\
    \gantttitlelist{13,...,20}{1} \\
%%%%%%% Phase 2
\ganttbar{ }{2017-06-01}{2017-06-30}  %elem0
\ganttmilestone{Proposal}{2017-06-30} \ganttnewline  %elem1
\ganttgroup{Dissertation Era}{2017-07-1}{2018-01-01} \\  %elem2
\ganttbar{Time Stepping}{2017-07-01}{2017-08-01} \ganttnewline  %elem3
\ganttlinkedbar{Uncert. Prop}{2017-08-01}{2017-09-01} \ganttnewline  %elem4
\ganttbar{Methods Refinement}{2017-08-01}{2017-10-01} \ganttnewline  %elem5
\ganttbar{Final CFD Runs}{2017-10-01}{2017-11-01} \ganttnewline  %elem6
\ganttbar{Write Dissertation}{2017-10-01}{2017-12-15}  %elem7
\ganttmilestone{Defense}{2017-12-15} \ganttnewline  %elem8
\ganttlinkedbar{Final Revisions}{2018-01-01}{2018-01-30}  \ganttnewline  %elem9
\ganttmilestone{Project Conclusion}{2018-01-30} \ganttnewline  %elem10
%%%%%%%% Extra Task Linkages
\end{ganttchart}
%-----------------------------------------------------------------------------%
\end{sidewaysfigure}


\pagebreak
